Combine_results

### 2017-02-23 Code/combine_results.Rmd
updating ms

completed.states <- included.states[c(1:4, 17:24)]
```

@@

# COD.levels <- c("Cardiovascular", "Cancers", "Communicable", 
#                 "Non-communicable", "Injuries", "All other causes")

#cod_decomp_results$COD <- factor(cod_decomp_results$COD, COD.levels)
age_cod_results$COD <- factor(age_cod_results$COD, levels = 1:6, 
                               labels = c("All other causes", "Cancers", "Cardiovascular", "Communicable",
                                          "Injuries", "Non-communicable"))

>>>>

completed.states <- included.states[c(1:11, 14, 17:24, 26:27, 33:34)]
```

@@

age_cod_results$COD <- factor(age_cod_results$COD, levels = 1:6, 
                               labels = c("All other causes", "Cancers", "Cardiovascular", "Communicable",
                                          "Injuries", "Non-communicable"))
